Finding ARG1 of Partitive Nouns in NomBank with DistilBERT

### 2022-05-04 src/paper.tex
Update

\begin{document}
\maketitle
\begin{abstract}
  This document is a supplement to the general instructions for *ACL authors. It contains instructions for using the \LaTeX{} style files for ACL conferences.
  The document itself conforms to its own specifications, and is therefore an example of what your manuscript should look like.
  These instructions should be used both for papers submitted for review and for final versions of accepted papers.
\end{abstract}

@@

More recently, the NLP community has seen huge popularity in heavily adopting pretraining-based langauge models. BERT (Devlin et al., 2018) is a large-size language representation model trained on a large corpus of English text that can achieve state-of-the-art results on a variety of natural language processing tasks. BERT came a decade later than the release of NomBank and there's been little previous work using it to conduct NomBank-based tasks and related experiments. However, as powerful as BERT is, its large parameters size makes it significantly more computationally expensive to train and use. On the other hand, DistilBERT is a distilled student model of BERT that retains 97\% of BERT's language understanding capabilities while being 40\% smaller and 60\% faster. This makes it a great candidate to train when facing with limited resources.

This paper presents a token classification approach using pre-trained DistilBERT to find ARG1 of partitive nouns in NomBank. It focuses on partitive nouns (nouns that are used to describe a part or quantity of something) and the partitive task. The task is described as finding one argument (ARG1) of \% (the percent sign), or in other words, finding the none group that is being sub-divided or quantified over. For example, for the sentence "Output in the energy sector rose 3.8\%.", the ARG1 to be found is "Output" since it is the partitive noun that "3.8\%" is referring to. This task can be translated into a binary classification problem on each token in the sentence where the model predicts whether the token is an ARG1 or not.

In addition to the token classification approach above, this paper also experiments with question-answer task, transforming the original ARG1 finding task into the task of make the model answer the question "What is the ARG1 of this sentence?". The advantage of this adaptation is that the model would stably output exactly one ARG1 for each sentence whereas token classification could give each sentence 0 to N ARG1s.

@@

BERT, or Bidirectional Encoder Representations from Transformers (Devlin et al., 2018), has shown state-of-the-art results on many NLP tasks. There have been many attempts to compress BERT into a smaller model, among which DistilBERT (Sanh et al., 2019) successfully reduces the size of a BERT model by 40\%, while retaining 97\% of its language understanding capabilities and being 60\% faster, leveraging  knowledge distillation (Bucila et al., 2006, Hinton et al., 2015) during the pre-training phase.

@@

@@

@@

The output of the question-answering model is the location (start index and end index) of the predicted answer. By locating the token on the original input token list with the start index and end index, we can reconstruct the ARG1 label of the sentence. The answer relocation is a bit more complicated due to the tokenization discrepancies between the original input and the tokenized input. This is explained in detailed in section \ref{section:data-preprocessing}.

@@

\section*{Acknowledgements}

@@

\appendix

\section{Example Appendix}
\label{sec:appendix}

This is an appendix.

>>>>

\begin{document}
\maketitle
\begin{abstract}
  This paper presents our attempts of multiple pipelines to find ARG1 of partitive nouns in NomBank with DistilBERT. NomBank is an annotation project at New York University based on Penn Treebank II corpus. Finding ARG1 of partitive nouns in the databank is an semantic role labeling (SRL) problem, which here we treated as a token classification task or a question-answering task. We adopted a knowledge-distilled version of BERT, DistilBERT, into our SRL pipeline, leveraging the knowledge of English Wikipedia and Toronto Book Corpus that the model was originally trained on. For the \% dataset, we achieved an F1 score of 0.9267 on the test set. And for the partitive dataset, we achieved an F1 score of 0.7945 on the test set.
\end{abstract}

@@

More recently, the NLP community has seen huge popularity in heavily adopting pretraining-based langauge models in attempt to transfer knowledge learned from large corpus into more specific tasks. BERT (Devlin et al., 2018) is a large-size language representation model trained on a large corpus of English text that can achieve state-of-the-art results on a variety of natural language processing tasks. BERT came a decade later than the release of NomBank and there's been little previous work using it to conduct NomBank-based tasks and related experiments. However, as powerful as BERT is, its large parameters size makes it significantly more computationally expensive to train and use. On the other hand, DistilBERT is a distilled student model of BERT that retains 97\% of BERT's language understanding capabilities while being 40\% smaller and 60\% faster. This makes it a great candidate to train when facing with limited resources.

This paper presents multiple token classification approaches using pre-trained DistilBERT to find ARG1 of partitive nouns in NomBank. It focuses on partitive nouns (nouns that are used to describe a part or quantity of something) and the partitive task. The task is described as finding one argument (ARG1) of \% (the percent sign), or in other words, finding the none group that is being sub-divided or quantified over. For example, for the sentence "Output in the energy sector rose 3.8\%.", the ARG1 to be found is "Output" since it is the partitive noun that "3.8\%" is referring to. This task can be translated into a binary classification problem on each token in the sentence where the model predicts whether the token is an ARG1 or not.

In addition to the token classification approaches above, this paper also experiments with question-answer task, transforming the original ARG1 finding task into the task of make the model answer the question "What is the ARG1 of this sentence?". The advantage of this adaptation is that the model would stably output exactly one ARG1 for each sentence whereas token classification could give each sentence 0 to N ARG1s.

@@

BERT, or Bidirectional Encoder Representations from Transformers (Devlin et al., 2018), has shown state-of-the-art results on many NLP tasks. The BERT base model has 110 million trainable parameters and was trained on a concentration of English Wikipedia and Toronto Book Corpus. There have been many attempts to compress BERT into a smaller model, among which DistilBERT (Sanh et al., 2019) successfully reduces the size of a BERT model by 40\%, while retaining 97\% of its language understanding capabilities and being 60\% faster, leveraging  knowledge distillation (Bucila et al., 2006, Hinton et al., 2015) during the pre-training phase.

@@

However, the NomBank dataset provisions text as already tokenized. The way the tokenizer provided by DistilBERT is often more fine-grained than how the NomBank dataset provides the text, causing some aligning issues. We fix this by align the tokens using \verb|word_ids| in the tokenization output. This is explained in detailed in section \ref{section:data-preprocessing}.

@@

In practice, this pipeline has the tendency of over predicting ARG1 labels. It predicts on a per-token basis, making classification of whether the token is an ARG1 or not on every token, thus possibly producing 0 to multiple ARG1s in one sentence. It is shown by our experiments that the deep models are more common to produce more than 1 ARG1s in one sentence. The ground truth, however, is one and only one ARG1 per sentence. A treatment of this inconsistency is to always force one ARG1 by the logits output of the deep neural network. We assign the token with the largest logit value in the output vector for the whole sentence to be the ARG1.

@@

The output of the question-answering model is the location (start index and end index) of the predicted answer. By locating the token on the original input token list with the start index and end index, we can reconstruct the ARG1 label of the sentence. The answer relocation is a bit more complicated due to the tokenization discrepancies between the original input and the tokenized input. Again, this is explained in detailed in section \ref{section:data-preprocessing}.

@@

\section{Experiment Results}

\begin{table*}
  \centering
  \begin{tabular}{c||c|c|c}
    \hline
    \textbf{Model}        & \textbf{Precision} & \textbf{Recall} & \textbf{F1-Score} \\
    \hline
    MaxEnt Baseline       & {71.88\%}          & {61.33\%}       & {66.19\%}         \\
    DistilBERT            & {93.75\%}          & {90.00\%}       & {91.84\%}         \\
    DistilBERT (POS+BIO)  & {93.19\%}          & {91.33\%}       & {92.25\%}         \\
    DistilBERT (QA)       & {92.00\%}          & {92.00\%}       & {92.00\%}         \\
    DistilBERT (ONE ARG1) & {92.67\%}          & {92.67\%}       & {92.67\%}         \\
    \hline
  \end{tabular}
  \caption{Precision, Recall and F1-Score on the \% dataset}
  \label{tab:results-on-first-dataset}
\end{table*}

\begin{table*}
  \centering
  \begin{tabular}{c||c|c|c}
    \hline
    \textbf{Model}  & \textbf{Precision} & \textbf{Recall} & \textbf{F1-Score} \\
    \hline
    MaxEnt Baseline & {55.33\%}          & {36.02\%}       & {43.64\%}         \\
    DistilBERT      & {80.49\%}          & {78.43\%}       & {79.45\%}         \\
    \hline
  \end{tabular}
  \caption{Precision, Recall and F1-Score on the partitive dataset}
  \label{tab:results-on-partitive-dataset}
\end{table*}

\section{Conclusion}

\section{Future Work}

\section*{References}

@@
